Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-05-23 paper/manuscript.Rmd
add some more references (ind diff book)

<!-- ## How has it been measured traditionally? -->
One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does]. 
Here, children watch a short sequence of events (often acted out or narrated by the experimenters). 
A doll called Sally puts her marble into a basket. 
After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box. 
Participants then get asked where Sally will look for her marble once she returns. 
The outcome measures false belief understanding in a dichotomous way: 
children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket. 
Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysisa]. 
Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. 
As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.

@@

However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure]. 
For example, those identifiers could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual]. 
Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency. 
For this endeavor, we need to take individual differences seriously – both theoretically and methodologically.

<!-- ## Existing research tapping into individual differences -->
Some studies have already examined individual differences in social cognition [@hughes2015individual; @slaughter2015theorya]. 
Previous studies focused, for example, 
on the association of mental state talk and false belief understanding [@hughes2011individual], 
emotion, language, family interaction, and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], 
stereotypes and theory of mind [@rizzo2018theory], 
prosociality and theory of mind [for a review, see @imuta2016theory; @walker2005gender], 
executive functions and theory of mind [@carlson2004individual; @buttelmann2021relations], 
parenting practices and theory of mind [for a review, see @pavarini2013parental], 
agency and moral cognition [@sodian2016understanding], 
attachment quality and gaze following [@astor2020social], 
language and gaze following [@okumura2017individual], 
and the interplay of physical and social cognition [@herrmann2010structure]. 
Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].

<!-- ## Methodological limitations -->
Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related [e.g., @sodian2016understanding]. 
This might be because traditional measures of social cognition are not designed to capture variation between children: 
they often rely on low trial numbers, small sample sizes, and dichotomous measures. 
@hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies. 
The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed "reliability paradox"). 
Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest].

Even studies focusing on individual differences often use behavioral forced-choice paradigms [e.g., carlson2004individual; @walker2005gender]. 
Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual]. 
This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations]. 
This has profound implications for what these studies can show. 
Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

@@

Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic]. 
Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual]. 
@schaafsma2015deconstructing proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.

Another goal in creating new tasks should be to focus on the face value: 
we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. 
The task should serve as a proxy for behavior as it appears in the real world. 
Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.

@@

## Limitations
## Future development / extending the task

>>>>

<!-- ## How has it been measured traditionally? -->
One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task [@baron-cohen1985does]. 
Here, children watch a short sequence of events (often acted out or narrated by the experimenters). 
A doll called Sally puts her marble into a basket. 
After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box. 
Participants then get asked where Sally will look for her marble once she returns. 
The outcome measures false belief understanding in a dichotomous way: 
children pass the task if they take the protagonist’s epistemic state into account and answer that she will look into the basket. 
Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age [for a review, see @wellman2001metaanalysisa]. 
Several cross-cultural studies supported this evidence [@barrett2013early; @callaghan2005synchrony; cf. @mayer2015weird].
However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. 
As @wellman2012theory put it, “it’s really only passing/failing one sort of understanding averaged across age” (p. 317). 
Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.

@@

However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions [@happe2017structure]. 
For example, the structure of variability could be used to provide evidence for two accounts: (1) *developmental lags* (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) *genuine variation* (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) [@hughes2015individual]. @stenhaug2021structure have argued for the differentiation between stage models (i.e., synchronization in developmental changes across distinct domains) and modular theories (i.e., particular aspects of development proceed on their own schedule). 
In addition, individual difference studies are useful for identifying antecedent factors as potential developmental causes, consequences of an early or late social-cognitive development, and qualitative differences in the actual social life [@keenan2003individual; @bartsch1996individual]. 
Therefore, we argue that studying the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency requires us to take individual differences seriously – both theoretically and methodologically.

<!-- ## Existing research tapping into individual differences -->
Some studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. 
These individual differences studies usually focus on three different kinds of relationships between social-cognitive abilities and: 
(1) family influences, (2) other cognitive constructs, and (3) social outcome measures [for an overview, see @repacholi2003introduction].

The first subgroup covers studies on social-cognitive abilities and parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background (education, occupation, sibling interaction, childcare) [@dunn1991young; @cutting1999theory; bulgarelli2016social]. 
In the second subgroup, individual differences studies include the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins]. 
The third subgroup encompasses studies on social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], 
stereotypes and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].

<!-- ## Methodological limitations -->
Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related [e.g., @sodian2016understanding]. 
This might be because traditional measures of social cognition are not designed to capture variation between children: 
they often rely on low trial numbers, small sample sizes, and dichotomous measures. 
@hedge2018reliability argued that cognitive tasks often become well-established by displaying robust effects across studies. 
The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed "reliability paradox"). 
Similarly, @pronk2021methods reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties [@beaudoin2020systematic] or showed poor test-retest reliability [@mayes1996testretest] [but cf @hughes2000good].

Even studies focusing on individual differences often use behavioral forced-choice paradigms [e.g., carlson2004individual; @walker2005gender]. 
Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error [@hughes2011individual]. 
This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis [e.g., @bulgarelli2016social; @rizzo2018theory; @buttelmann2021relations]. In addition, individual differences are only identified in the age of onset of the social-cognitive ability and not in performance or competence [@repacholi2003introduction]. 
This has profound implications for what these studies can show. 
Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

@@

Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum [@hughes2015individual; @beaudoin2020systematic; @keenan2003individual]. 
Task batteries might be better suited to cover a range of social-cognitive abilities [@hughes2011individual, @repacholi2003introduction]. 
@schaafsma2015deconstructing proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.

Another goal in creating new tasks should be to focus on the face value: 
we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. 
The task should serve as a proxy for behavior as it appears in the real world [@repacholi2003introduction; @repacholi2004individual]. 
Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.

@@

- benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)

## Limitations
## Future development / extending the task
- benefits of task battery

### 2022-05-23 paper/manuscript.tex
add some more references (ind diff book)

Social cognition - representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C. Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; Wellman, Cross, \& Watson, 2001; Wellman \& Liu, 2004).

One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
A doll called Sally puts her marble into a basket.
After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
Participants then get asked where Sally will look for her marble once she returns.
The outcome measures false belief understanding in a dichotomous way:
children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see Wellman et al., 2001).
Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value.
As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.

@@

However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
For example, those identifiers could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015).
Therefore, we argue that we should study the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.
For this endeavor, we need to take individual differences seriously -- both theoretically and methodologically.

Some studies have already examined individual differences in social cognition (Hughes \& Devine, 2015; Slaughter, 2015).
Previous studies focused, for example,
on the association of mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011),
emotion, language, family interaction, and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991),
stereotypes and theory of mind (Rizzo \& Killen, 2018),
prosociality and theory of mind (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
executive functions and theory of mind (Buttelmann, Kühn, \& Zmyj, 2021; Carlson, Moses, \& Claxton, 2004),
parenting practices and theory of mind (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013),
agency and moral cognition (Sodian et al., 2016),
attachment quality and gaze following (Astor et al., 2020),
language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017),
and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010).
Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007; Underwood, 1975).

Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related (e.g., Sodian et al., 2016).
This might be because traditional measures of social cognition are not designed to capture variation between children:
they often rely on low trial numbers, small sample sizes, and dichotomous measures.
Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed ``reliability paradox'').
Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996).

Even studies focusing on individual differences often use behavioral forced-choice paradigms {[}e.g., carlson2004individual; Walker (2005){]}.
Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018).
This has profound implications for what these studies can show.
Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

@@

Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015).
Task batteries might be better suited to cover a range of social-cognitive abilities (Hughes et al., 2011).
Schaafsma et al. (2015) proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.

Another goal in creating new tasks should be to focus on the face value:
we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
The task should serve as a proxy for behavior as it appears in the real world.
Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
Carlson, S. M., Moses, L. J., \& Claxton, L. J. (2004). Individual differences in executive functioning and theory of mind: {An} investigation of inhibitory control and planning ability. \emph{Journal of Experimental Child Psychology}, \emph{87}(4), 299--319. \url{https://doi.org/10.1016/j.jecp.2004.01.002}

@@

@@

@@

@@

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-wellman2001metaanalysisa}{}}%
Wellman, H. M., Cross, D., \& Watson, J. (2001). Meta-{Analysis} of {Theory-of-Mind Development}: {The Truth} about {False Belief}. \emph{Child Development}, \emph{72}(3), 655--684. \url{https://doi.org/10.1111/1467-8624.00304}

\leavevmode\vadjust pre{\hypertarget{ref-wellman2004scalinga}{}}%
Wellman, H. M., \& Liu, D. (2004). Scaling of {Theory-of-Mind Tasks}. \emph{Child Development}, \emph{75}(2), 523--541. \url{https://doi.org/10.1111/j.1467-8624.2004.00691.x}

>>>>

Social cognition - representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior - is among the most-studied phenomena in developmental research.
In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development (Gopnik \& Slaughter, 1991; Candida C. Peterson, Wellman, \& Slaughter, 2012; Rakoczy, 2022; \textbf{wellman2001metaanalysisa?}; \textbf{wellman2004scalinga?}).

One of the most commonly applied prototypical measures for social cognition is the Sally-Anne task (Baron-Cohen, Leslie, \& Frith, 1985).
Here, children watch a short sequence of events (often acted out or narrated by the experimenters).
A doll called Sally puts her marble into a basket.
After Sally leaves the scene, a second doll named Anne takes the marble and moves it into a box.
Participants then get asked where Sally will look for her marble once she returns.
The outcome measures false belief understanding in a dichotomous way:
children pass the task if they take the protagonist's epistemic state into account and answer that she will look into the basket.
Many years of research utilizing these verbal change-of-location tasks suggest that children develop belief-representing abilities at four to five years of age (for a review, see \textbf{wellman2001metaanalysisa?}).
Several cross-cultural studies supported this evidence (Barrett et al., 2013; Callaghan et al., 2005; cf. Mayer \& Träuble, 2015).
However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value (V. S. \&. B. Repacholi, 2003).
As Wellman (2012) put it, ``it's really only passing/failing one sort of understanding averaged across age'' (p.~317).
Therefore, the focus has been to track change at an (age-) group level within a narrow developmental time frame and with a strong emphasis on a single social-cognitive ability.

@@

However, identifying variability in social-cognitive abilities and factors influencing those could be vital in theory building (e.g., to test causal predictions) and design interventions (Happé et al., 2017).
For example, the structure of variability could be used to provide evidence for two accounts: (1) \emph{developmental lags} (i.e., whether children differ in their speed of acquiring new conceptual insights into the understanding of the mind), and (2) \emph{genuine variation} (i.e., whether children differ in their ease or fluency in (applying) these social-cognitive abilities) (Hughes \& Devine, 2015). Stenhaug, Ram, and Frank (2021) have argued for the differentiation between stage models (i.e., synchronization in developmental changes across distinct domains) and modular theories (i.e., particular aspects of development proceed on their own schedule).
In addition, individual difference studies are useful for identifying antecedent factors as potential developmental causes, consequences of an early or late social-cognitive development, and qualitative differences in the actual social life (Bartsch \& Estes, 1996; Keenan, 2003).
Therefore, we argue that studying the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency requires us to take individual differences seriously -- both theoretically and methodologically.

Some studies have already examined individual differences in social cognition (for an overview, see Hughes \& Devine, 2015; Slaughter, 2015).
These individual differences studies usually focus on three different kinds of relationships between social-cognitive abilities and:
(1) family influences, (2) other cognitive constructs, and (3) social outcome measures (for an overview, see V. S. \&. B. Repacholi, 2003).

The first subgroup covers studies on social-cognitive abilities and parenting practices (for a review, see Pavarini, de Hollanda Souza, \& Hawk, 2013), attachment quality (e.g., Astor et al., 2020), mental state talk (Gola, 2012; Hughes, Ensor, \& Marks, 2011; Lecce, Bianco, Devine, Hughes, \& Banerjee, 2014), and family background (education, occupation, sibling interaction, childcare) {[}Dunn, Brown, Slomkowski, Tesla, and Youngblade (1991); Cutting and Dunn (1999); bulgarelli2016social{]}.
In the second subgroup, individual differences studies include the interplay of social and physical cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010), executive functions (Benson, Sabbagh, Carlson, \& Zelazo, 2012; Buttelmann, Kühn, \& Zmyj, 2021; Stephanie M. Carlson \& Moses, 2001; Stephanie M. Carlson, Moses, \& Claxton, 2004; Hughes \& Ensor, 2007), and language abilities (McEwen et al., 2007 Mar-Apr; Milligan, Astington, \& Dack, 2007; Okumura, Kanakogi, Kobayashi, \& Itakura, 2017).
The third subgroup encompasses studies on social cognition and prosociality (for a review, see Imuta, Henry, Slaughter, Selcuk, \& Ruffman, 2016; Walker, 2005),
stereotypes and resource allocations (Rizzo \& Killen, 2018), and moral intentions (Sodian et al., 2016).

Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd et al., 2018; Mundy et al., 2007; Underwood, 1975).

Frequently, developmental psychologists are surprised to find minor or no association between constructs that are thought to be theoretically related (e.g., Sodian et al., 2016).
This might be because traditional measures of social cognition are not designed to capture variation between children:
they often rely on low trial numbers, small sample sizes, and dichotomous measures.
Hedge, Powell, and Sumner (2018) argued that cognitive tasks often become well-established by displaying robust effects across studies.
The authors could show that this usually does not emerge due to high measurement variance but relatively low between-subject variability, concluding that popular cognitive tasks may reliably measure group differences but not individual differences (termed ``reliability paradox'').
Similarly, Pronk, Molenaar, Wiers, and Murre (2021) reasoned that accurate reliability estimates are needed to judge how well a particular cognitive test is suited to draw inferences about individuals.
A recent review underlined reoccurring issues in standardization, validity, reliability, and sensitivity to developmental change: alarmingly few theory of mind measures reported empirically validated psychometric properties (Beaudoin, Leblanc, Gagner, \& Beauchamp, 2020) or showed poor test-retest reliability (Mayes, Klin, Tercyak, Cicchetti, \& Cohen, 1996) (but cf Hughes et al., 2000).

Even studies focusing on individual differences often use behavioral forced-choice paradigms {[}e.g., carlson2004individual; Walker (2005){]}.
Few studies that do realize continuous measures often administer (theory of mind) scales and conventionally compute aggregate scores (across tasks or trials), therefore neglecting the issue of measurement error (Hughes et al., 2011).
This way, a particular social-cognitive ability in question is still assessed categorically on a trial basis (e.g., Bulgarelli \& Molina, 2016; Buttelmann et al., 2021; Rizzo \& Killen, 2018). In addition, individual differences are only identified in the age of onset of the social-cognitive ability and not in performance or competence (V. S. \&. B. Repacholi, 2003).
This has profound implications for what these studies can show.
Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

@@

Additionally, it has been argued that social-cognitive abilities should not be treated as an all-or-nothing matter (e.g., dichotomously in pass/fail situations) but as abilities on a continuum (Beaudoin et al., 2020; Hughes \& Devine, 2015; Keenan, 2003).
Task batteries might be better suited to cover a range of social-cognitive abilities V. S. \&. B. Repacholi (2003).
Schaafsma et al. (2015) proposed that first basic social-cognitive processes should be relatively well understood before advancing to more complex social-cognitive abilities.

Another goal in creating new tasks should be to focus on the face value:
we want to measure the underlying social-cognitive ability as straight-forward and directly as possible.
The task should serve as a proxy for behavior as it appears in the real world (B. Repacholi \& Slaughter, 2004; V. S. \&. B. Repacholi, 2003).
Importantly, we can assess whether the task shows external validity by evaluating the relationship with related constructs and factors of children's social surroundings.

@@

\begin{itemize}
\tightlist
\item
  benefits of hedge (psychometric properties) vs box (discrete, easier for kids to click, induce salience etc)
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  benefits of task battery
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-bartsch1996individual}{}}%
Bartsch, K., \& Estes, D. (1996). Individual differences in children's developing theory of mind and implications for metacognition. \emph{Learning and Individual Differences}, \emph{8}(4), 281--304. \url{https://doi.org/10.1016/S1041-6080(96)90020-5}

@@

\leavevmode\vadjust pre{\hypertarget{ref-benson2012individual}{}}%
Benson, J., Sabbagh, M., Carlson, S., \& Zelazo, P. (2012). Individual {Differences} in {Executive Functioning Predict Preschoolers}' {Improvement From Theory-of-Mind Training}. \emph{Developmental Psychology}, \emph{49}. \url{https://doi.org/10.1037/a0031056}

@@

\leavevmode\vadjust pre{\hypertarget{ref-carlson2001individual}{}}%
Carlson, Stephanie M., \& Moses, L. J. (2001). Individual {Differences} in {Inhibitory Control} and {Children}'s {Theory} of {Mind}. \emph{Child Development}, \emph{72}(4), 1032--1053.

\leavevmode\vadjust pre{\hypertarget{ref-carlson2004individual}{}}%
Carlson, Stephanie M., Moses, L. J., \& Claxton, L. J. (2004). Individual differences in executive functioning and theory of mind: {An} investigation of inhibitory control and planning ability. \emph{Journal of Experimental Child Psychology}, \emph{87}(4), 299--319. \url{https://doi.org/10.1016/j.jecp.2004.01.002}

@@

\leavevmode\vadjust pre{\hypertarget{ref-gola2012mental}{}}%
Gola, A. A. H. (2012). Mental verb input for promoting children's theory of mind: {A} training study. \emph{Cognitive Development}, \emph{27}(1), 64--76. \url{https://doi.org/10.1016/j.cogdev.2011.10.003}

@@

\leavevmode\vadjust pre{\hypertarget{ref-hughes2000good}{}}%
Hughes, C., Adlam, A., Happé, F., Jackson, J., Taylor, A., \& Caspi, A. (2000). Good {Test}-{Retest Reliability} for {Standard} and {Advanced False}-{Belief Tasks} across a {Wide Range} of {Abilities}. \emph{Journal of Child Psychology and Psychiatry}, \emph{41}(4), 483--490. \url{https://doi.org/10.1111/1469-7610.00633}

@@

\leavevmode\vadjust pre{\hypertarget{ref-hughes2007executive}{}}%
Hughes, C., \& Ensor, R. (2007). Executive function and theory of mind: {Predictive} relations from ages 2 to 4. \emph{Developmental Psychology}, \emph{43}(6), 1447--1459. \url{https://doi.org/10.1037/0012-1649.43.6.1447}

@@

\leavevmode\vadjust pre{\hypertarget{ref-keenan2003individual}{}}%
Keenan, T. (2003). Individual {Differences} in {Theory} of {Mind}: {The Preschool Years} and {Beyond}. In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-lecce2014promoting}{}}%
Lecce, S., Bianco, F., Devine, R. T., Hughes, C., \& Banerjee, R. (2014). Promoting theory of mind during middle childhood: {A} training program. \emph{Journal of Experimental Child Psychology}, \emph{126}, 52--67. \url{https://doi.org/10.1016/j.jecp.2014.03.002}

@@

\leavevmode\vadjust pre{\hypertarget{ref-mcewen2007origins}{}}%
McEwen, F., Happé, F., Bolton, P., Rijsdijk, F., Ronald, A., Dworzynski, K., \& Plomin, R. (2007 Mar-Apr). Origins of individual differences in imitation: Links with language, pretend play, and socially insightful behavior in two-year-old twins. \emph{Child Development}, \emph{78}(2), 474--492. \url{https://doi.org/10.1111/j.1467-8624.2007.01010.x}

\leavevmode\vadjust pre{\hypertarget{ref-milligan2007language}{}}%
Milligan, K., Astington, J. W., \& Dack, L. A. (2007). Language and {Theory} of {Mind}: {Meta-Analysis} of the {Relation Between Language Ability} and {False-belief Understanding}. \emph{Child Development}, \emph{78}(2), 622--646. \url{https://doi.org/10.1111/j.1467-8624.2007.01018.x}

@@

\leavevmode\vadjust pre{\hypertarget{ref-repacholi2004individual}{}}%
Repacholi, B., \& Slaughter, V. (Eds.). (2004). \emph{Individual {Differences} in {Theory} of {Mind}} (Zeroth). {New York}: {Psychology Press}. \url{https://doi.org/10.4324/9780203488508}

\leavevmode\vadjust pre{\hypertarget{ref-repacholi2003introduction}{}}%
Repacholi, V. S. \&. B. (2003). Introduction {Individual Differences} in {Theory} of {Mind}: {What Are We Investigating}? In \emph{Individual {Differences} in {Theory} of {Mind}}. {Psychology Press}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-stenhaug2021structure}{}}%
Stenhaug, B., Ram, N., \& Frank, M. C. (2021). \emph{The {Structure} of {Developmental Variation} in {Early Childhood}}. {PsyArXiv}. \url{https://doi.org/10.31234/osf.io/95erq}

@@
